Curvature Enhance with Laplacian Operator for Hybrid Quad/Triangle Meshes

### 2013-01-04 trunk/documents/thesis/TQLBO-paper/Paper-Siggraph/paper.tex

%% LyX 2.0.2 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[english,annual]{acmsiggraph}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{amssymb}
\usepackage{graphicx}

@@

This work is organized as follows: In the section \ref{sub:1.1-Related-work}
show works related to the Laplacian mesh processing, digital sculpting,
and offsetting methods for polygonal meshes; In the section \ref{sec:Laplacian-Smooth}
we describe the theoretical framework of the Laplacian operator for
polygon meshes; In the section \ref{sec:Proposed-Method} we present
our proposed method for curvature enhancement and applications on
subdivision surfaces and sculpting; Lastly some results are shown
in graphic examples of Laplacian operator for polygonal meshes composed
of triangles and quads. Also shows some results of curvature enhancement
applications in sculpting, subdivision and modeling methods.

\textbf{Contributions} Our work present an extension of the Laplace
Beltrami operator for meshes of arbitrary topology composed for triangles
and quads representing a larger spectrum of mesh that works with today
eliminating the need for preprocessing and allows the preservation
of the original topology. With this operator we proposed a method
to generate family of parameterized shapes, in a robust and predictable
way. Our method enable to customization of smoothness and curvature
obtained during subdivision surfaces process. We proposed a new brush
for enhance silhouette features of mesh in modeling and sculpting.

@@

\subsection{Laplace Beltrami operator over triangular and quadrilateral meshes
TQLBO\label{sub:Laplace-Beltrami-operator}}

@@

The area of $1$-ring neighborhood ($N_{1}$) with shared face to
vertex $v_{i}$ in $M$ is.

@@

Where $q_{1},q_{2},...,q_{i},...,q_{m}\in Q_{N_{1}\left(v_{i}\right)}$
and $t_{1},t_{2},...,t_{k},...,t_{r}\in T_{N_{1}\left(v_{i}\right)}$.

@@

All triangles and quads configurations of the 1-neighborhood faces
adjacent to $v_{i}$ can be simplified in five simple cases how show
in figure \ref{fig:LBO-basic-5-TQ}.

@@

Where $L$ is the $n\times n$ matrix, $n$ is the number of vertices
of a given mesh $M$, $w_{ij}$ is the TQLBO defined in equation (\ref{eq:TQLBO_wij}),
$N\left(v_{i}\right)$ is the 1-ring neighbors with shared face to
$v_{i}$, $A_{i}$ is the ring area around $v_{i}$.

@@

The model volume increases as the lambda is most negative, this can
be countered by a simple method of preserving volume. In \cite{Desbrun1999}
present a simple method to resize the mesh but have a problem the
model suffer large displacements with $\lambda<-1.0$ or perform multiple
iterations. We propose the following solution: If we have $v_{i}^{t+1}$
is a mesh vertex of $V^{t+1}$ in the $t+1$ iteration.

@@

The Catmull-Clark subdivision transformation is used to smooth a surface
as the limit of sequence of subdivision steps\cite{Stam1998}. This
method do a recursive subdivision transformation that refines the
model into a linear interpolation that is a approximate smooth surface.
The process of Catmull-Clark is govern by properties of B-spline curve
from multivariate spline theory\cite{Loop1987}. In many subdivision
surfaces methods Catmull-Clark, Loop so on. The smoothness of the
model is automatically guaranteed\cite{DeRose1998}.

Catmull-Clark subdivision surface method generates smooth and continuous
models from a coarse model and produce results quickly due to the
simplicity of implementation, but with these methods is not easy to
make changes to the global curvature of the model. If we use Catmull-Clark
subdivision surfaces and curvature enhancement for modeling from sketches
with few vertices can generate families of shapes with just a parameter,
which would allow an artist to choose the model of a similar set of
options that best meets your needs without having to change each one
of the control vertices.

@@

In this section we describe the results of our curvature enhance method
that used our extension of Laplace Beltrami operator for triangles
and quads TQLBO with several example models in figures \ref{fig:Spectrum},\ref{fig:camello_enhanced}.
We test the curvature enhance with TQLBO method on a PC with AMD Quad-Core
Processor @ 2.40 GHz and 8 GB RAM.

Figure \ref{fig:TQLBO_test} show the results when applying Laplacian
smoothing operator TQLBO of equation (\ref{eq:TQLBO_Simple_Matrix})
in a model with a simple subdivision. In column (c) Laplacian smoothing
was applied to the model consists of only quads. In column (d) the
model was converted to triangles and then Laplacian smoothing was
applied. In column (e) the model is converted randomly some quads
into triangles and then Laplacian smoothing was applied, showing similar
results to those composed only of triangles or squares.

@@

Figure \ref{fig:Sculpt_Brush} shows the use of curvature enhancement
locally in real time. One pass was used with the brush as shown in
the figure with the blue and red radius. In the bottom of the figure
\ref{fig:Sculpt_Brush}.b shows how the camel leg self-intersecting
and looks like two bubbles stuck, so do the fingers on the bottom
of figure. Using silhouette features enhancement in figure \ref{fig:Sculpt_Brush}.c
we see better results because not lost the shape of the silhouette
and kept the details of the fingers and leg. Similar results can be
obtained by an artist but it would take several steps and the use
of several brushes with curvatures enhancement only takes one step.
With this new method can easily enhance organic features how muscles
during the sculpting process. In figure \ref{fig:Performance-sculpt}
we show the performance of curvature enhancement brush, in this experimet
we use three models with 12K, 40K and 164K this models were sculpted
with curvature enhance brush in eache step the brush sphere contain
a variable number of vertices for processing. The processing time
for 800 vertices in the camel paw (40k model) only take 0.1 seconds,
for 2600 vertices in leg and neck (model 40k) take 0.5 seconds, these
times are good, because usually an artist sculpts a model for parts,
and each part is represented by an average of about 3000 vertices
in the models we use.

>>>>

%% LyX 2.0.4 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[english,annual]{acmsiggraph}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{amssymb}
\usepackage{graphicx}

@@

This work is organized as follows: In the section \ref{sub:1.1-Related-work}
show works related to the Laplacian mesh processing, digital sculpting,
and offsetting methods for polygonal meshes; In the section \ref{sec:Laplacian-Smooth}
we describe the theoretical framework of the Laplacian operator for
polygon meshes; In the section \ref{sec:Proposed-Method} we present
our proposed method for curvature enhancement and applications on
subdivision surfaces and sculpting; Lastly some results are shown
in graphic examples of Laplacian operator for hybrid quad/triangle
meshes. Also shows some results of curvature enhancement applications
in sculpting, subdivision and modeling methods.

\textbf{Contributions} Our work present an extension of the Laplace
Beltrami operator for hybrid quad/triangle meshes representing a larger
spectrum of mesh that works with today eliminating the need for preprocessing
and allows the preservation of the original topology. With this operator
we proposed a method to generate family of parameterized shapes, in
a robust and predictable way. Our method enable to customization of
smoothness and curvature obtained during subdivision surfaces process.
We proposed a new brush for enhance silhouette features of mesh in
modeling and sculpting.

@@

\subsection{Laplace Beltrami Operator for Hybrid Quad/Triangle Meshes TQLBO\label{sub:Laplace-Beltrami-operator}}

@@

The area of $1$-ring neighborhood ($N_{1}$) with shared face quad
or triangle to vertex $v_{i}$ in $M$ is.

@@

Where $q_{1},q_{2},...,q_{j},...,q_{m}\in Q_{N_{1}\left(v_{i}\right)}$
and $t_{1},t_{2},...,t_{k},...,t_{r}\in T_{N_{1}\left(v_{i}\right)}$.

@@

All triangles and quads configurations of the 1-ring neighborhood
faces adjacent to $v_{i}$ can be simplified in five simple cases
how show in figure \ref{fig:LBO-basic-5-TQ}.

@@

Where $L$ is the $n\times n$ matrix, $n$ is the number of vertices
of a given mesh $M$, $w_{ij}$ is the TQLBO defined in equation (\ref{eq:TQLBO_wij}),
$N\left(v_{i}\right)$ is the 1-ring neighborhood with shared face
to $v_{i}$, $A_{i}$ is the ring area around $v_{i}$.

@@

The model volume increases as the lambda is most negative, this can
be countered by a simple method of preserving volume. In \cite{Desbrun1999}
present a simple method to resize the mesh but have a problem the
model suffer large displacements with $\lambda<-1.0$ or perform multiple
iterations. We propose the following solution: If we have $v_{i}^{t+1}$
is a mesh vertex of $V^{t+1}$ in the $t+1$ iteration, we define
$\overline{v}$ as:

@@

The Catmull-Clark subdivision transformation is used to smooth a surface
as the limit of sequence of subdivision steps\cite{Stam1998}. This
method do a recursive subdivision transformation that refines the
model into a linear interpolation that is a approximate smooth surface.
The process of Catmull-Clark is govern by properties of B-spline curve
from multivariate spline theory\cite{Loop1987}. In many subdivision
surfaces methods Catmull-Clark, Loop so on, the smoothness of the
model is automatically guaranteed \cite{DeRose1998}.

Catmull-Clark subdivision surface method generates smooth and continuous
models from a coarse model and produce results quickly due to the
simplicity of implementation, but with these methods is not easy to
make changes to the global curvature of the model. If we use Catmull-Clark
subdivision surfaces and curvature enhancement for modeling from coarse
models with few vertices can generate families of shapes with just
change a parameter, which would allow an artist to choose the model
of a similar set of options that best meets your needs without having
to change each one of the control vertices.

@@

In this section we describe the results of our curvature enhance method
that used our extension of Laplace Beltrami operator for hybrid quad/triangle
meshes with several example models in figures \ref{fig:Spectrum},
\ref{fig:Subdivision-Cups}, \ref{fig:Catmull_Clark}, \ref{fig:TQLBO_test},
\ref{fig:camello_enhanced}, \ref{fig:Sculpt_Brush}, \ref{fig:Performance-sculpt},
\ref{fig:(a)Monkey}, \ref{fig:Animated_Camell}. We test the curvature
enhance with TQLBO method on a PC with AMD Quad-Core Processor @ 2.40
GHz and 8 GB RAM.

Figure \ref{fig:TQLBO_test} show the results when applying Laplace
Beltrami Operator TQLBO of equation (\ref{eq:TQLBO_Simple_Matrix})
in a model with a simple subdivision. In column (c) Laplacian smoothing
was applied to the model consists of only quads. In column (d) the
model was converted to triangles and then Laplacian smoothing was
applied. In column (e) the model is converted randomly some quads
into triangles and then Laplacian smoothing was applied, showing similar
results to those composed only of triangles or squares.

@@

Figure \ref{fig:Sculpt_Brush} shows the use of curvature enhancement
brush for sculpting in real time. One pass was used with the brush
as shown in the figure with the blue and red radius. In the bottom
of the figure \ref{fig:Sculpt_Brush}.b shows how the camel leg self-intersecting
and looks like two bubbles stuck, so do the fingers on the bottom
of figure. Using silhouette features enhancement in figure \ref{fig:Sculpt_Brush}.c
we see better results because not lost the shape of the silhouette
and kept the details of the fingers and leg. Similar results can be
obtained by an artist but it would take several steps and the use
of several brushes with curvatures enhancement only takes one step.
With this new method can easily enhance organic features how muscles
during the sculpting process. In figure \ref{fig:Performance-sculpt}
we show the performance of curvature enhancement brush, in this experimet
we use three models with 12K, 40K and 164K vertices, this models were
sculpted with curvature enhance brush in eache step the brush sphere
contain a variable number of vertices for processing. The processing
time for 800 vertices in the camel paw (40k model) only take 0.1 seconds,
for 2600 vertices in leg and neck (model 40k) take 0.5 seconds, these
times are good, because usually an artist sculpts a model for parts,
and each part is represented by an average of about 3000 vertices
in the models we use.
